---
title: "core_pred_cm"
output: html_document
---

```{r}
#rm(list = ls())
#ugh, visualizing these will be fun...
#first run just with everything, duplication type one hot encoding
#credit to https://stackoverflow.com/questions/37897252/plot-confusion-matrix-in-r-using-ggplot
#install.packages("gridExtra")

library(tidyverse)
library(ggplot2)
library(gridExtra)

wkdir="./00_collab/02_core_pred/11_CM/"

cm_df = read.table(file = paste0(wkdir,"/cm_table_21_04_23.txt"), header = F, sep = "\t")

header = c("Model", "Train", "Test", "TN_avg", "TN_std", "FP_avg", "FP_std",
				"FN_avg", "FN_std", "TP_avg", "TP_std")

colnames(cm_df) = header

#try getting on plot object with confusion matrix package.. shit probs can't handle the plus/minus should probs just do this manually huh
plot_confusion_matrix = function(df = df, model = model, train_sp = train_sp, 
                                test_sp = test_sp) {
  #just go with averages and ignore stdev for now
  #customized function for our confusion matricies
  #subset data frame
  sub_df = df[which(df$Model == model & df$Train == train_sp & df$Test == test_sp),]
  
  if (nrow(sub_df) != 1) {
    stop(paste0("unable to get single row for ", model, " ", train_sp, " ", test_sp))
  }

  sub_table = data.frame(Prediction = factor(c("Core", "Disp", "Core", "Disp")),
                      Reference = factor(c("Core", "Core", "Disp", "Disp")),
                      Freq = c(sub_df$TP_avg[1], sub_df$FN_avg[1], 
                               sub_df$FP_avg[1], sub_df$TN_avg[1]))
  out_df = sub_table %>%
    mutate(goodbad = ifelse(table$Prediction == table$Reference, "good", "bad")) %>%
    group_by(Reference) %>%
    mutate(prop = Freq/sum(Freq))
  
  out_plot = ggplot(data = out_df, mapping = aes(x = Reference, y = Prediction, fill = goodbad, alpha = prop)) +
    geom_tile() +
    geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1, size = 2) +
    scale_fill_manual(values = c(good = "green", bad = "red")) +
    theme_bw() +
    xlim(rev(levels(sub_table$Reference))) +
    ggtitle(paste0(model, " ", train_sp, " ", test_sp)) +
    theme(legend.position = "none",
          title = element_text(size = 5))
  
  return(out_plot)

}

rft_osat_osat_cm_plot = plot_confusion_matrix(df = cm_df, model = "RFT", train_sp = "Osat",
                                        test_sp = "Osat")

#hmm make list of plots, lets just do two by two to start then can expand
rft_plot_list = list()
svc_plot_list = list()
gnb_plot_list = list()
train_list = c("Osat","Bdis","Osat_Bal","Bdis_Bal","BdisA","BdisA_Bal")
test_list = c("Osat","Bdis","Osat_Bal","Bdis_Bal","BdisA","BdisA_Bal")
i = 1
for (train_sp in train_list) {
  for (test_sp in test_list) {
    rft_plot_list[[i]] = plot_confusion_matrix(df = cm_df, model = "RFT", 
                                           train_sp = train_sp, test_sp = test_sp)
    svc_plot_list[[i]] = plot_confusion_matrix(df = cm_df, model = "SVC", 
                                           train_sp = train_sp, test_sp = test_sp)
    gnb_plot_list[[i]] = plot_confusion_matrix(df = cm_df, model = "GNB", 
                                           train_sp = train_sp, test_sp = test_sp)
    i = i + 1
  }
}


height = 8
width = 8
png(filename = paste0(wkdir,"/osat_bdis_bdisA_cm_rft.png"), width = width, height = height,
    units = "in", res = 300)
  grid.arrange(rft_plot_list[[1]],rft_plot_list[[2]],rft_plot_list[[3]],
             rft_plot_list[[4]],rft_plot_list[[5]],rft_plot_list[[6]],
             rft_plot_list[[7]],rft_plot_list[[8]],rft_plot_list[[9]],
             rft_plot_list[[10]],rft_plot_list[[11]],rft_plot_list[[12]],
             rft_plot_list[[13]],rft_plot_list[[14]],rft_plot_list[[15]],
             rft_plot_list[[16]],rft_plot_list[[17]],rft_plot_list[[18]],
             rft_plot_list[[19]],rft_plot_list[[20]],rft_plot_list[[21]],
             rft_plot_list[[22]],rft_plot_list[[23]],rft_plot_list[[24]],
             rft_plot_list[[25]],rft_plot_list[[26]],rft_plot_list[[27]],
             rft_plot_list[[28]],rft_plot_list[[29]],rft_plot_list[[30]],
             rft_plot_list[[31]],rft_plot_list[[32]],rft_plot_list[[33]],
             rft_plot_list[[34]],rft_plot_list[[35]],rft_plot_list[[36]],
             nrow = 6)
dev.off()

png(filename = paste0(wkdir,"/osat_bdis_bdisA_cm_svc.png"), width = width, height = height,
    units = "in", res = 300)
  grid.arrange(svc_plot_list[[1]],svc_plot_list[[2]],svc_plot_list[[3]],
             svc_plot_list[[4]],svc_plot_list[[5]],svc_plot_list[[6]],
             svc_plot_list[[7]],svc_plot_list[[8]],svc_plot_list[[9]],
             svc_plot_list[[10]],svc_plot_list[[11]],svc_plot_list[[12]],
             svc_plot_list[[13]],svc_plot_list[[14]],svc_plot_list[[15]],
             svc_plot_list[[16]],svc_plot_list[[17]],svc_plot_list[[18]],
             svc_plot_list[[19]],svc_plot_list[[20]],svc_plot_list[[21]],
             svc_plot_list[[22]],svc_plot_list[[23]],svc_plot_list[[24]],
             svc_plot_list[[25]],svc_plot_list[[26]],svc_plot_list[[27]],
             svc_plot_list[[28]],svc_plot_list[[29]],svc_plot_list[[30]],
             svc_plot_list[[31]],svc_plot_list[[32]],svc_plot_list[[33]],
             svc_plot_list[[34]],svc_plot_list[[35]],svc_plot_list[[36]],
             nrow = 6)
dev.off()


png(filename = paste0(wkdir,"/osat_bdis_bdisA_cm_gnb.png"), width = width, height = height,
    units = "in", res = 300)
  grid.arrange(gnb_plot_list[[1]],gnb_plot_list[[2]],gnb_plot_list[[3]],
             gnb_plot_list[[4]],gnb_plot_list[[5]],gnb_plot_list[[6]],
             gnb_plot_list[[7]],gnb_plot_list[[8]],gnb_plot_list[[9]],
             gnb_plot_list[[10]],gnb_plot_list[[11]],gnb_plot_list[[12]],
             gnb_plot_list[[13]],gnb_plot_list[[14]],gnb_plot_list[[15]],
             gnb_plot_list[[16]],gnb_plot_list[[17]],gnb_plot_list[[18]],
             gnb_plot_list[[19]],gnb_plot_list[[20]],gnb_plot_list[[21]],
             gnb_plot_list[[22]],gnb_plot_list[[23]],gnb_plot_list[[24]],
             gnb_plot_list[[25]],gnb_plot_list[[26]],gnb_plot_list[[27]],
             gnb_plot_list[[28]],gnb_plot_list[[29]],gnb_plot_list[[30]],
             gnb_plot_list[[31]],gnb_plot_list[[32]],gnb_plot_list[[33]],
             gnb_plot_list[[34]],gnb_plot_list[[35]],gnb_plot_list[[36]],
             nrow = 6)
dev.off()

```


#messin with some stack overflow suggestions
```{r}
install.packages("caret")
install.packages("e1071")
library(caret)
library(e1071)

lvs <- c("normal", "abnormal")
truth <- factor(rep(lvs, times = c(86, 258)),
                levels = rev(lvs))
pred <- factor(
  c(
    rep(lvs, times = c(54, 32)),
    rep(lvs, times = c(27, 231))),
  levels = rev(lvs))

confusionMatrix(pred, truth)

table <- data.frame(confusionMatrix(pred, truth)$table)

plotTable <- table %>%
  mutate(goodbad = ifelse(table$Prediction == table$Reference, "good", "bad")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))
ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = goodbad, alpha = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1) +
  scale_fill_manual(values = c(good = "green", bad = "red")) +
  theme_bw() +
  xlim(rev(levels(table$Reference)))

plotTable
#   Prediction Reference  Freq goodbad  prop
#   <fct>      <fct>     <int> <chr>   <dbl>
# 1 abnormal   abnormal    231 good    0.895
# 2 normal     abnormal     27 bad     0.105
# 3 abnormal   normal       32 bad     0.372
# 4 normal     normal       54 good    0.628

sub_confusion_matrix = function(df = df, model = model, train_sp = train_sp, 
                                test_sp = test_sp) {
  #just go with averages and ignore stdev for now
  #customized function for our confusion matricies
  #subset data frame
  sub_df = df[which(df$Model == model & df$Train == train_sp & df$Test == test_sp),]
  
  if (nrow(sub_df) != 1) {
    stop(paste0("unable to get single row for ", model, " ", train_sp, " ", test_sp))
  }

  sub_table = data.frame(Prediction = c("Core", "Disp", "Core", "Disp"),
                      Reference = c("Core", "Core", "Disp", "Disp"),
                      Freq = c(sub_df$TP_avg[1], sub_df$FN_avg[1], 
                               sub_df$FP_avg[1], sub_df$TN_avg[1]))
  out_df = sub_table %>%
  mutate(goodbad = ifelse(table$Prediction == table$Reference, "good", "bad")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))
  
  return(out_df)

}


```




#no Ka/Ks included..
#I mean just has to be a balancing issue right?
```{r}
#rm(list = ls())
#ugh, visualizing these will be fun...
#first run just with everything, duplication type one hot encoding
#credit to https://stackoverflow.com/questions/37897252/plot-confusion-matrix-in-r-using-ggplot
#install.packages("gridExtra")

library(tidyverse)
library(ggplot2)
library(gridExtra)

wkdir="./00_collab/02_core_pred/11_CM/"

cm_df = read.table(file = paste0(wkdir,"/cm_table_no_ka_ks_21_04_23.txt"), header = F, sep = "\t")

header = c("Model", "Train", "Test", "TN_avg", "TN_std", "FP_avg", "FP_std",
				"FN_avg", "FN_std", "TP_avg", "TP_std")

colnames(cm_df) = header

#try getting on plot object with confusion matrix package.. shit probs can't handle the plus/minus should probs just do this manually huh
plot_confusion_matrix = function(df = df, model = model, train_sp = train_sp, 
                                test_sp = test_sp) {
  #just go with averages and ignore stdev for now
  #customized function for our confusion matricies
  #subset data frame
  sub_df = df[which(df$Model == model & df$Train == train_sp & df$Test == test_sp),]
  
  if (nrow(sub_df) != 1) {
    stop(paste0("unable to get single row for ", model, " ", train_sp, " ", test_sp))
  }

  sub_table = data.frame(Prediction = factor(c("Core", "Disp", "Core", "Disp")),
                      Reference = factor(c("Core", "Core", "Disp", "Disp")),
                      Freq = c(sub_df$TP_avg[1], sub_df$FN_avg[1], 
                               sub_df$FP_avg[1], sub_df$TN_avg[1]))
  out_df = sub_table %>%
    mutate(goodbad = ifelse(table$Prediction == table$Reference, "good", "bad")) %>%
    group_by(Reference) %>%
    mutate(prop = Freq/sum(Freq))
  
  out_plot = ggplot(data = out_df, mapping = aes(x = Reference, y = Prediction, fill = goodbad, alpha = prop)) +
    geom_tile() +
    geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1, size = 2) +
    scale_fill_manual(values = c(good = "green", bad = "red")) +
    theme_bw() +
    xlim(rev(levels(sub_table$Reference))) +
    ggtitle(paste0(model, " ", train_sp, " ", test_sp)) +
    theme(legend.position = "none",
          title = element_text(size = 5))
  
  return(out_plot)

}

#rft_osat_osat_cm_plot = plot_confusion_matrix(df = cm_df, model = "RFT", train_sp = "Osat",
#                                        test_sp = "Osat")

#hmm make list of plots, lets just do two by two to start then can expand
rft_plot_list = list()
svc_plot_list = list()
gnb_plot_list = list()
train_list = c("Osat","Bdis","Osat_Bal","Bdis_Bal","BdisA","BdisA_Bal")
test_list = c("Osat","Bdis","Osat_Bal","Bdis_Bal","BdisA","BdisA_Bal")
i = 1
for (train_sp in train_list) {
  for (test_sp in test_list) {
    rft_plot_list[[i]] = plot_confusion_matrix(df = cm_df, model = "RFT", 
                                           train_sp = train_sp, test_sp = test_sp)
    svc_plot_list[[i]] = plot_confusion_matrix(df = cm_df, model = "SVC", 
                                           train_sp = train_sp, test_sp = test_sp)
    gnb_plot_list[[i]] = plot_confusion_matrix(df = cm_df, model = "GNB", 
                                           train_sp = train_sp, test_sp = test_sp)
    i = i + 1
  }
}


height = 8
width = 8
png(filename = paste0(wkdir,"/osat_bdis_bdisA_cm_no_ka_ks_rft.png"), width = width, height = height,
    units = "in", res = 300)
  grid.arrange(rft_plot_list[[1]],rft_plot_list[[2]],rft_plot_list[[3]],
             rft_plot_list[[4]],rft_plot_list[[5]],rft_plot_list[[6]],
             rft_plot_list[[7]],rft_plot_list[[8]],rft_plot_list[[9]],
             rft_plot_list[[10]],rft_plot_list[[11]],rft_plot_list[[12]],
             rft_plot_list[[13]],rft_plot_list[[14]],rft_plot_list[[15]],
             rft_plot_list[[16]],rft_plot_list[[17]],rft_plot_list[[18]],
             rft_plot_list[[19]],rft_plot_list[[20]],rft_plot_list[[21]],
             rft_plot_list[[22]],rft_plot_list[[23]],rft_plot_list[[24]],
             rft_plot_list[[25]],rft_plot_list[[26]],rft_plot_list[[27]],
             rft_plot_list[[28]],rft_plot_list[[29]],rft_plot_list[[30]],
             rft_plot_list[[31]],rft_plot_list[[32]],rft_plot_list[[33]],
             rft_plot_list[[34]],rft_plot_list[[35]],rft_plot_list[[36]],
             nrow = 6)
dev.off()

png(filename = paste0(wkdir,"/osat_bdis_bdisA_cm_no_ka_ks_svc.png"), width = width, height = height,
    units = "in", res = 300)
  grid.arrange(svc_plot_list[[1]],svc_plot_list[[2]],svc_plot_list[[3]],
             svc_plot_list[[4]],svc_plot_list[[5]],svc_plot_list[[6]],
             svc_plot_list[[7]],svc_plot_list[[8]],svc_plot_list[[9]],
             svc_plot_list[[10]],svc_plot_list[[11]],svc_plot_list[[12]],
             svc_plot_list[[13]],svc_plot_list[[14]],svc_plot_list[[15]],
             svc_plot_list[[16]],svc_plot_list[[17]],svc_plot_list[[18]],
             svc_plot_list[[19]],svc_plot_list[[20]],svc_plot_list[[21]],
             svc_plot_list[[22]],svc_plot_list[[23]],svc_plot_list[[24]],
             svc_plot_list[[25]],svc_plot_list[[26]],svc_plot_list[[27]],
             svc_plot_list[[28]],svc_plot_list[[29]],svc_plot_list[[30]],
             svc_plot_list[[31]],svc_plot_list[[32]],svc_plot_list[[33]],
             svc_plot_list[[34]],svc_plot_list[[35]],svc_plot_list[[36]],
             nrow = 6)
dev.off()


png(filename = paste0(wkdir,"/osat_bdis_bdisA_cm_no_ka_ks_gnb.png"), width = width, height = height,
    units = "in", res = 300)
  grid.arrange(gnb_plot_list[[1]],gnb_plot_list[[2]],gnb_plot_list[[3]],
             gnb_plot_list[[4]],gnb_plot_list[[5]],gnb_plot_list[[6]],
             gnb_plot_list[[7]],gnb_plot_list[[8]],gnb_plot_list[[9]],
             gnb_plot_list[[10]],gnb_plot_list[[11]],gnb_plot_list[[12]],
             gnb_plot_list[[13]],gnb_plot_list[[14]],gnb_plot_list[[15]],
             gnb_plot_list[[16]],gnb_plot_list[[17]],gnb_plot_list[[18]],
             gnb_plot_list[[19]],gnb_plot_list[[20]],gnb_plot_list[[21]],
             gnb_plot_list[[22]],gnb_plot_list[[23]],gnb_plot_list[[24]],
             gnb_plot_list[[25]],gnb_plot_list[[26]],gnb_plot_list[[27]],
             gnb_plot_list[[28]],gnb_plot_list[[29]],gnb_plot_list[[30]],
             gnb_plot_list[[31]],gnb_plot_list[[32]],gnb_plot_list[[33]],
             gnb_plot_list[[34]],gnb_plot_list[[35]],gnb_plot_list[[36]],
             nrow = 6)
dev.off()

```


#get tables for supplement, just reference genotype for bdis sooo 4x4?
```{r}
#rm(list = ls())
#ugh, visualizing these will be fun...
#first run just with everything, duplication type one hot encoding
#credit to https://stackoverflow.com/questions/37897252/plot-confusion-matrix-in-r-using-ggplot
#install.packages("gridExtra")

library(tidyverse)
library(ggplot2)
library(gridExtra)

wkdir="./00_collab/02_core_pred/11_CM/"

cm_df = read.table(file = paste0(wkdir,"/cm_table_21_04_30.txt"), header = F, sep = "\t")

header = c("Model", "Train", "Test", "TN_avg", "TN_std", "FP_avg", "FP_std",
				"FN_avg", "FN_std", "TP_avg", "TP_std")

colnames(cm_df) = header

#try getting on plot object with confusion matrix package.. shit probs can't handle the plus/minus should probs just do this manually huh
plot_confusion_matrix = function(df = df, model = model, train_sp = train_sp, 
                                test_sp = test_sp) {
  #just go with averages and ignore stdev for now
  #customized function for our confusion matricies
  #subset data frame
  sub_df = df[which(df$Model == model & df$Train == train_sp & df$Test == test_sp),]
  
  if (nrow(sub_df) != 1) {
    stop(paste0("unable to get single row for ", model, " ", train_sp, " ", test_sp))
  }

  sub_table = data.frame(Prediction = factor(c("Core", "Disp", "Core", "Disp")),
                      Reference = factor(c("Core", "Core", "Disp", "Disp")),
                      Freq = c(sub_df$TP_avg[1], sub_df$FN_avg[1], 
                               sub_df$FP_avg[1], sub_df$TN_avg[1]))
  out_df = sub_table %>%
    mutate(goodbad = ifelse(sub_table$Prediction == sub_table$Reference, "good", "bad")) %>%
    group_by(Reference) %>%
    mutate(prop = Freq/sum(Freq))
  
  out_plot = ggplot(data = out_df, mapping = aes(x = Reference, y = Prediction, fill = goodbad, alpha = prop)) +
    geom_tile() +
    geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1, size = 2) +
    scale_fill_manual(values = c(good = "green", bad = "red")) +
    theme_bw() +
    xlim(rev(levels(sub_table$Reference))) +
    ggtitle(paste0(model, " ", train_sp, " ", test_sp)) +
    theme(legend.position = "none",
          title = element_text(size = 5))
  
  return(out_plot)

}


#hmm make list of plots, lets just do two by two to start then can expand
rft_plot_list = list()
svc_plot_list = list()
gnb_plot_list = list()
train_list = c("Osat","Bdis","Osat_Bal","Bdis_Bal")
test_list = c("Osat","Bdis","Osat_Bal","Bdis_Bal")
i = 1
for (train_sp in train_list) {
  for (test_sp in test_list) {
    rft_plot_list[[i]] = plot_confusion_matrix(df = cm_df, model = "RFT", 
                                           train_sp = train_sp, test_sp = test_sp)
    svc_plot_list[[i]] = plot_confusion_matrix(df = cm_df, model = "SVC", 
                                           train_sp = train_sp, test_sp = test_sp)
    gnb_plot_list[[i]] = plot_confusion_matrix(df = cm_df, model = "GNB", 
                                           train_sp = train_sp, test_sp = test_sp)
    i = i + 1
  }
}


height = 8
width = 8
png(filename = paste0(wkdir,"/osat_bdis_cm_rft.png"), width = width, height = height,
    units = "in", res = 300)
  grid.arrange(rft_plot_list[[1]],rft_plot_list[[2]],rft_plot_list[[3]],
             rft_plot_list[[4]],rft_plot_list[[5]],rft_plot_list[[6]],
             rft_plot_list[[7]],rft_plot_list[[8]],rft_plot_list[[9]],
             rft_plot_list[[10]],rft_plot_list[[11]],rft_plot_list[[12]],
             rft_plot_list[[13]],rft_plot_list[[14]],rft_plot_list[[15]],
             rft_plot_list[[16]],
             nrow = 4)
dev.off()

png(filename = paste0(wkdir,"/osat_bdis_cm_svc.png"), width = width, height = height,
    units = "in", res = 300)
  grid.arrange(svc_plot_list[[1]],svc_plot_list[[2]],svc_plot_list[[3]],
             svc_plot_list[[4]],svc_plot_list[[5]],svc_plot_list[[6]],
             svc_plot_list[[7]],svc_plot_list[[8]],svc_plot_list[[9]],
             svc_plot_list[[10]],svc_plot_list[[11]],svc_plot_list[[12]],
             svc_plot_list[[13]],svc_plot_list[[14]],svc_plot_list[[15]],
             svc_plot_list[[16]],
             nrow = 4)
dev.off()


png(filename = paste0(wkdir,"/osat_bdis_cm_gnb.png"), width = width, height = height,
    units = "in", res = 300)
  grid.arrange(gnb_plot_list[[1]],gnb_plot_list[[2]],gnb_plot_list[[3]],
             gnb_plot_list[[4]],gnb_plot_list[[5]],gnb_plot_list[[6]],
             gnb_plot_list[[7]],gnb_plot_list[[8]],gnb_plot_list[[9]],
             gnb_plot_list[[10]],gnb_plot_list[[11]],gnb_plot_list[[12]],
             gnb_plot_list[[13]],gnb_plot_list[[14]],gnb_plot_list[[15]],
             gnb_plot_list[[16]],
             nrow = 4)
dev.off()

```

sessionInfo()
R version 4.0.3 (2020-10-10)
Platform: x86_64-apple-darwin17.0 (64-bit)
Running under: macOS Catalina 10.15.7

Matrix products: default
BLAS:   /System/Library/Frameworks/Accelerate.framework/Versions/A/Frameworks/vecLib.framework/Versions/A/libBLAS.dylib
LAPACK: /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRlapack.dylib

locale:
[1] en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base     

other attached packages:
 [1] multipanelfigure_2.1.2 gridExtra_2.3          e1071_1.7-6            caret_6.0-86          
 [5] lattice_0.20-41        forcats_0.5.1          stringr_1.4.0          dplyr_1.0.4           
 [9] purrr_0.3.4            readr_1.4.0            tidyr_1.1.2            tibble_3.0.6          
[13] ggplot2_3.3.3          tidyverse_1.3.0        phytools_0.7-70        maps_3.3.0            
[17] ape_5.4-1             

loaded via a namespace (and not attached):
 [1] assertive.base_0.0-9       colorspace_2.0-0           ellipsis_0.3.1            
 [4] class_7.3-17               fs_1.5.0                   rstudioapi_0.13           
 [7] proxy_0.4-25               farver_2.0.3               prodlim_2019.11.13        
[10] fansi_0.4.2                lubridate_1.7.9.2          xml2_1.3.2                
[13] codetools_0.2-16           splines_4.0.3              mnormt_2.0.2              
[16] knitr_1.31                 jsonlite_1.7.2             pROC_1.17.0.1             
[19] broom_0.7.4                dbplyr_2.1.0               compiler_4.0.3            
[22] httr_1.4.2                 backports_1.2.1            assertthat_0.2.1          
[25] Matrix_1.2-18              cli_2.4.0                  htmltools_0.5.1.1         
[28] tools_4.0.3                igraph_1.2.6               coda_0.19-4               
[31] gtable_0.3.0               glue_1.4.2                 reshape2_1.4.4            
[34] clusterGeneration_1.3.7    tinytex_0.29               fastmatch_1.1-0           
[37] Rcpp_1.0.6                 cellranger_1.1.0           vctrs_0.3.6               
[40] nlme_3.1-149               assertive.files_0.0-2      iterators_1.0.13          
[43] timeDate_3043.102          gower_0.2.2                xfun_0.20                 
[46] rvest_0.3.6                lifecycle_1.0.0            phangorn_2.5.5            
[49] gtools_3.8.2               MASS_7.3-53                scales_1.1.1              
[52] ipred_0.9-11               hms_1.0.0                  parallel_4.0.3            
[55] expm_0.999-6               yaml_2.2.1                 rpart_4.1-15              
[58] stringi_1.5.3              foreach_1.5.1              plotrix_3.8-1             
[61] lava_1.6.9                 rlang_0.4.10               pkgconfig_2.0.3           
[64] evaluate_0.14              assertive.properties_0.0-4 recipes_0.1.16            
[67] labeling_0.4.2             tidyselect_1.1.0           plyr_1.8.6                
[70] magrittr_2.0.1             R6_2.5.0                   magick_2.6.0              
[73] generics_0.1.0             combinat_0.0-8             DBI_1.1.1                 
[76] pillar_1.4.7               haven_2.3.1                withr_2.4.1               
[79] assertive.numbers_0.0-2    survival_3.2-7             scatterplot3d_0.3-41      
[82] nnet_7.3-14                modelr_0.1.8               crayon_1.4.0              
[85] assertive.types_0.0-3      utf8_1.1.4                 tmvnsim_1.0-2             
[88] rmarkdown_2.6              grid_4.0.3                 readxl_1.3.1              
[91] data.table_1.14.0          ModelMetrics_1.2.2.2       reprex_1.0.0              
[94] digest_0.6.27              numDeriv_2016.8-1.1        gridGraphics_0.5-1        
[97] stats4_4.0.3               munsell_0.5.0              quadprog_1.5-8 

